Concurrent Programming with CXL

### 2020-06-05 book/paper.tex
Latest

We can do this by adding another process that, in a loop,
checks the invariant.  Figure~\ref{fig:tasinv} shows the code.
Method \texttt{checkInvariant()} checks to see if the invariant holds
in a state.  It introduces a new feature of CXL: the ability to have
variables local to a method.  In this case, the variable \texttt{sum}
is used to compute the number of variables that have value
\texttt{False}.
The function is invoked by in a loop by a process that runs alongside
the other processes.
In CXL, \texttt{assert} statements are executed atomically, so the
evaluation of the assertion is not interleaved with the execution
of other processes.
Because CXL tries every possible execution, the process is guaranteed
to find violations of the invariant if it does not hold.

@@

\begin{quote}
\begin{itemize}
\item Draw additional states and steps in Figure~\ref{fig:rdwr} to 
for three processes.
\end{itemize}
\end{quote}

>>>>

We can do this by adding another process that, in a loop,
checks the invariant.  Figure~\ref{fig:tasinv} shows the code.
Method \texttt{checkInvariant()} checks to see if the invariant holds
in a state.  It introduces a new feature of CXL: the ability to have
variables local to a method.  In this case, the process variable \texttt{sum}
is used to compute the number of shared variables that have value
\texttt{False}.
The function is invoked by in a loop by a process that runs alongside
the other processes.
In CXL, \texttt{assert} statements are executed atomically, so the
evaluation of the assertion is not interleaved with the execution
of other processes.
Because CXL tries every possible execution, the process is guaranteed
to find violations of the invariant if it does not hold.

@@

\begin{quote}
\begin{itemize}
\item Draw additional states and steps in Figure~\ref{fig:rdwr}
for three processes.
\end{itemize}
\end{quote}
